### 2016-08-05 notions.tex
cheers
playing with notions again

\tsnote{Is this the right kind of indistinguishability anyway?  This current notion says, in effect, that $S_0$ and $S_1$ are indistinguishable \emph{with respect to the allowed queries} (assuming that $\pubaux$ doesn't stupidly leak information.)  But why not try to formalize the intution that a representation~$M$ and the public info~$\pubaux$ tell you nothing (non-trivial) about the set being represented, period?  (Classical BFs, by the way, essentially leak the number of elements in the set by looking at the number of 0-bits in the array.)   That's tricky to define... Also, if you give~$M$ to the adversary, how do you handle the fact that, under our current syntax, $M$~may contain secret keys, etc.?}
%\tsnote{How will the adversary know that a query satisfies
%  this in (say) the case of the classical BF?  We can, of course,
%enforce it in the experiment, but then our resource accounting risks
%overcounting the number of queries.} \jnote{I was assuming the attacker knows $S_0, S_1$.}
%\tsnote{Also, we need that, in general, $\aux$ itself
%does not leak information about~$S_0$ vs.\ $S_1$. } \jnote{Sure, this would be implied
%by the definition in this case.}
\end{enumerate}

\begin{figure}[htbp]
\centering
\hfpages{.495}{
\hpagess{.5}{.45}
{
\experimentv{$\ExpWPriv{\setprim,\distr{\calS}{}}{A}$}\\
$S \getsr \distr{\calS}{}$\\
$(M,\pubaux,\privaux) \getsr \Rep(S)$\\
$z \getsr A^{\TestOracle}(\pubaux)$\\
if $z \in S$ then Return 1\\
Return 0\\

\medskip
\experimentv{$\ExpPriv{\setprim,\distr{\calS}{}}{A}$}\\
$S \getsr \distr{\calS}{}$\\
$(M,\pubaux,\privaux) \getsr \Rep(S)$\\
$z \getsr A(M,\pubaux)$\\
if $z \in S$ then Return 1\\
Return 0\\
}
%
{
\oracle{$\TestOracle(q)$}\\
$a \gets \Qry(M,\aux,q)$\\
Return~$a$
}
}
%
{
\hpagess{.485}{.5}
{
\experimentv{$\ExpPrivInd{\setprim,\distr{\calS}{}}{A}$}\\
$b \getsr \bits$\\
$S_0,S_1 \getsr \distr{\calS}{}$\\
$(M,\pubaux,\privaux) \getsr \Rep(S_b)$\\
$b' \getsr A^{\TestOracle}(S_0,S_1,\pubaux)$\\
if $b' = b$ then Return 1\\
Return 0\\

\medskip
\experimentv{$\ExpPrivSS{\setprim,\distr{\calS}{}}{A}$}\\
$S \getsr \distr{\calS}{}$\\
$(M,\pubaux,\privaux) \getsr \Rep(S)$\\
$f \getsr A(M,\pubaux)$\\
$S' \getsr \distr{\calS}{}$\\
if $f(S) \neq f(S')$ then\\
\nudge Return 1\\
Return 0\\
}
%
{
\oracle{$\TestOracle(q)$}\\
$a \gets \Qry(M,\privaux,q)$\\
Return~$a$\\

%\medskip
%\oracle{$\RepOracle(S_0,S_1)$}\\
%f $\mathrm{used}=\true$ then Return $\bot$\\
%%if $|S_0|\neq|S_1|$ then \\
%%\nudge Ret $\bot$\\
%$S_0,S_1 \getsr \distr{\calS}{}$\\
%$\mathrm{used}=\true$\\
%$(M,\aux) \getsr \Rep(S_b)$\\
%Return $(S_0,S_1,\aux)$\\

}
}
\caption{Privacy notions. {\bf Left:} ``One-wayness'' style
  definitions. The top is a weaker notion, because the representation
  is hidden from the adversary. {\bf Right:} An
  ``indistinguishability'' style notion and a semantic-security style notion. (Still playing...)} 
\label{fig:privacy}
\end{figure}

>>>>

\tsnote{Is this the right kind of indistinguishability anyway?  This
  current notion says, in effect, that $S_0$ and $S_1$ are
  indistinguishable \emph{with respect to the allowed queries}
  (assuming that $\pubaux$ doesn't stupidly leak information.)  But
  why not try to formalize the intution that a representation~$M$ and
  the public info~$\pubaux$ tell you nothing (non-trivial) about the
  set being represented, period?  (Classical BFs, by the way,
  essentially leak the number of elements in the set by looking at the
  number of 0-bits in the array.)   That's tricky to define... I'll
  take a shot at it.}
%\tsnote{How will the adversary know that a query satisfies
%  this in (say) the case of the classical BF?  We can, of course,
%enforce it in the experiment, but then our resource accounting risks
%overcounting the number of queries.} \jnote{I was assuming the attacker knows $S_0, S_1$.}
%\tsnote{Also, we need that, in general, $\aux$ itself
%does not leak information about~$S_0$ vs.\ $S_1$. } \jnote{Sure, this would be implied
%by the definition in this case.}
\end{enumerate}

\begin{figure}[htbp]
\centering
\hfpages{.495}{
\hpagess{.5}{.45}
{
\experimentv{$\ExpPriv{\setprim,\distr{\calS}{}}{A}$}\\
$S \getsr \distr{\calS}{}$\\
$(M,\pubaux,\privaux) \getsr \Rep(S)$\\
$z \getsr A^{\TestOracle}(M,\pubaux)$\\
if $z \in S$ then Return 1\\
Return 0\\

\medskip
\experimentv{$\ExpWPriv{\setprim,\distr{\calS}{}}{A}$}\\
$S \getsr \distr{\calS}{}$\\
$(M,\pubaux,\privaux) \getsr \Rep(S)$\\
$z \getsr A^{\TestOracle}(\pubaux)$\\
if $z \in S$ then Return 1\\
Return 0\\
}
%
{
\oracle{$\TestOracle(q)$}\\
$a \gets \Qry(M,\privaux,q)$\\
Return~$a$
}
}
%
{
\hpagess{.485}{.5}
{
\experimentv{$\ExpPrivInd{\setprim,\distr{\calS}{}}{A}$}\\
$b \getsr \bits$\\
$S_0,S_1 \getsr \distr{\calS}{}$\\
$(M,\pubaux,\privaux) \getsr \Rep(S_b)$\\
$b' \getsr A^{\TestOracle}(M,\pubaux)$\\
if $b' = b$ then Return 1\\
Return 0\\

\medskip
\experimentv{$\ExpPrivSS{\setprim,\distr{\calS}{}}{A}$}\\
$S\getsr \distr{\calS}{}$\\
$(M,\pubaux,\privaux) \getsr \Rep(S)$\\
$f \getsr A(M,\pubaux,\privaux)$\\
$S' \getsr \distr{\calS}{}$\\
if $f(S) \neq f(S')$ then\\
\nudge Return 1\\
Return 0\\
}
%
{
\oracle{$\TestOracle(q)$}\\
$a \gets \Qry(M,\privaux,q)$\\
Return~$a$\\

%\medskip
%\oracle{$\RepOracle(S_0,S_1)$}\\
%if $\mathrm{used}=\true$ then Return $\bot$\\
%%if $|S_0|\neq|S_1|$ then \\
%%\nudge Ret $\bot$\\
%$S_0,S_1 \getsr \distr{\calS}{}$\\
%$\mathrm{used}=\true$\\
%$(M,\aux) \getsr \Rep(S_b)$\\
%Return $(S_0,S_1,\aux)$\\

}
}
\caption{Privacy notions. {\bf Left:} ``One-wayness'' style
  definitions. The bottom is a weaker notion, because the representation
  is hidden from the adversary. {\bf Right:} An
  ``indistinguishability'' style notion and a semantic-security style notion. (Still playing...)} 
\label{fig:privacy}
\end{figure}
